Review of Assigned Readings

### 2018-01-05 paper/paper.tex
adjusted Abstract

%************************** Abstract ************************** 
\begin{abstract}
\pagenumbering{Roman}
This paper, examines the dynamics between the amount of Twitter activity regarding Bitcoin and the actual price fluctuation of Bitcoin. For the analysis two sets of data have been collected. One reflecting Twitter activity and the other one showing the Bitcoin prices for the same period. Based on that an econometric model is used for the statistical analysis and the interpretation of the results.\\
The evaluation of the model showed that changes in Twitter activity on Bitcoin have a minimal and insignificant effect on the future price development of Bitcoin. Accordingly, aggregate Twitter fees are not a good source to predict changes in Bitcoin prices. This result must be understood with caution, because it only applies for the specific time interval of our observations, which is about 8 days and not for the past or future trend of cryptocurrencies. \\
This work was created in the context of a programming course for economists at the university of St. Gallen. To not exceed the framework of this study we require extensive knowledge in econometrics and take concepts as known. The underlying goal was to get familiar with software engineering tools and project management. Therefore, the academic content of this work is neither completed nor concluding.\\
\end{abstract}

@@

%************************** List of Figures ************************** 	
\listoffigures\bigskip\bigskip
\listoftables

>>>>

%************************** Abstract ************************** 
\begin{abstract}
\pagenumbering{Roman}
Based on previous research in the stock market, this paper uses a Twitter sentiment analysis to determine the dynamics between the amount of Twitter activity regarding Bitcoin and the market price of Bitcoin. The analysis is based on two different data sets. Twitter activity has been measured by the number of tweets containing the term "Bitcoin" while Bitcoin prices were measured in the Bitcoin price index. The Vector Autoregression (VAR) model was used for the statistical analysis and the interpretation of the results.\\

The evaluation of the econometric model showed that changes in Twitter activity on Bitcoin have only a minimal and insignificant effect on the future price development of Bitcoin. This result must be understood with caution, because it only applies for the specific time interval of 8 days in which Twitter data have been gathered. Further on, researchers are being encouraged to elaborate on our observations, by applying our methodology over a longer time period and for additional cryptocurrencies. \\

\end{abstract}

@@

%************************** List of Figures ************************** 	
\listoffigures\bigskip\bigskip

\listoftables
